Bioverse: The Habitable Zone Inner Edge Discontinuity as an Imprint of Runaway Greenhouse Climates on Exoplanet Demographics

### 2023-07-31 src/tex/ms.tex
cite Matuszewski et al. 2023

A successful transit detection requires a sufficient signal-to-noise ratio, which is sensitive to the achieved photometric precision. %~\citep[e.g.,][]{Koch2010,Ricker2014,Burke2015,Hardegree-Ullman2019} % Cabrera+ in prep for \plato\
%In its in-orbit commissioning phase, the \cheops\ mission demonstrated a photometric precision of \SI{75}{\ppm} for faint ($V\approx 12$) stars~\citep{Benz2021}.
%In comparison, \plato's expected precision for similar stars was estimated to be \SI{\sim 50}{\ppm}~\citep[][Matuszewski et al., in prep.]{plato2017}.
\plato\ (PLAnetary Transits and Oscillation of stars) is an ESA mission designed to characterize terrestrial planets in the habitable zones of Sun-like stars via long-term high-precision photometric monitoring of a sample of bright stars~\citep{Rauer2016}.
In line with this requirement, \plato\ is designed to enable the detection of a \SI{80}{\ppm} transit signal\rev{~\citep[][Matuszewski et al., subm.]{plato2017}}.
To reflect its sensitivity, we chose a minimum transit depth of \SI{80}{\ppm} as a detection limit and consider only measurements of planets exceeding this threshold.
We further exclude target stars with \gaia\ magnitudes $M_\mathrm{G} > \minMagnitude$.

>>>>

A successful transit detection requires a sufficient signal-to-noise ratio, which is sensitive to the achieved photometric precision. %~\citep[e.g.,][]{Koch2010,Ricker2014,Burke2015,Hardegree-Ullman2019} % Cabrera+ in prep for \plato\
%In its in-orbit commissioning phase, the \cheops\ mission demonstrated a photometric precision of \SI{75}{\ppm} for faint ($V\approx 12$) stars~\citep{Benz2021}.
%In comparison, \plato's expected precision for similar stars was estimated to be \SI{\sim 50}{\ppm}~\citep[][Matuszewski et al., in prep.]{plato2017}.
\plato\ (PLAnetary Transits and Oscillation of stars) is an ESA mission designed to characterize terrestrial planets in the habitable zones of Sun-like stars via long-term high-precision photometric monitoring of a sample of bright stars~\citep{Rauer2016}.
In line with this requirement, \plato\ is designed to enable the detection of a \SI{80}{\ppm} transit signal\rev{~\citep{Matuszewski2023,plato2017}}.
To reflect its sensitivity, we chose a minimum transit depth of \SI{80}{\ppm} as a detection limit and consider only measurements of planets exceeding this threshold.
We further exclude target stars with \gaia\ magnitudes $M_\mathrm{G} > \minMagnitude$.
